Design, Implementation, and Evaluation of Open Power Quality

### 2020-06-27 09-pilot.tex
final tweaks

Computational cost, is proportional to the amount of date acquired. Since the meter level analytics are at best only good enough for event detection, further analysis is required for event classification.
This implies that the OPQ Makai triggering algorithm is at least 8 times more efficient then the self triggered counterpart.
Furthermore, in the self triggered case, data at the lowest granularity consists of waveforms from an individual device.
These waveforms need to be matched together in order to extract grid-wide anomalies.
On the other hand, OPQ Makai events contain data from all devices which experienced an anomaly, thus saving additional CPU time.

>>>>

The computational cost of an OPQ sensor network is proportional to the amount of data acquired. Since the meter level analytics are at best only good enough for event detection, further analysis is required for event classification.
This implies that the OPQ Makai triggering algorithm is at least 8 times more efficient then the self triggered counterpart, since 8 times less data is sent by OPQ Boxes to the cloud for analysis.
